\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal]{IEEEtran}
\usepackage[a5paper, margin=10mm, onecolumn]{geometry}
%\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
% \usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{PH:PHYSICS-2014}
\author{AI24BTECH11005 - Bhukya Prajwal Naik
}
% \maketitle
% \newpage
% \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats


\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}


\begin{enumerate}
		\setcounter{enumi}{29}
    

 
%16
    \item  The donor concentration in a sample of n-type silicon is increased by a factor of 100. The shift in the position of the Fermi level at 300 K , assuming the sample to be non degenerate is $\qquad$ meV .
$$
(k_{B} T=25 {meV} \text { at } 300 {~K})
$$
   
        
  \item   A particle of mass $m$ is subjected to a potential,
$$
V(x, y)=\frac{1}{2} m \omega^{2}(x^{2}+y^{2}),-\infty \leq x \leq \infty,-\infty \leq y \leq \infty
$$

The state with energy $4 \hbar \omega$ is $g$-fold degenerate. The value of $g$ is $\qquad$ .
 
  
  \item A hydrogen atom is in the state
$\Psi=\sqrt{\frac{8}{21}} \psi_{200}-\sqrt{\frac{3}{7}} \psi_{310}+\sqrt{\frac{4}{21}} \psi_{321}$
where $n, l, m$ in $\psi_{n l m}$ denote the principal, orbital and magnetic quantum numbers, respectively. If $\vec{L}$ is the angular momentum operator, the average value of $L^{2}$ is $(\qquad$) $\hbar^{2}$\\\\
  
  \item A planet of mass $m$ moves in a circular orbit of radius $r_{0}$ in the gravitational potential $V(r)=-\frac{k}{r}$, where $k$ is a positive constant. The orbital angular momentum of the planet is
  \begin{multicols}{4}
			\begin{enumerate}
   \item $2 r_{0} {~km}$
\item $\sqrt{2 r_{0} k m}$
\item $r_{0} {~km}$
\item  $\sqrt{r_{0} k m}$
\end{enumerate}
		\end{multicols}
   
%33
\item The moment of inertia of a rigid diatomic molecule $A$ is 6 times that of another rigid diatomic molecule $B$. If the rotational energies of the two molecules are equal, then the corresponding values of the rotational quantum numbers $J_{{A}}$ and $J_{{B}}$ are
   \begin{multicols}{4}
			\begin{enumerate}
   \item $J_{{A}}=2, J_{{B}}=1$
\item  $J_{{A}}=3, J_{{B}}=1$
\item$J_{{A}}=5, J_{{B}}=0$
\item  $J_{A}=6, J_{B}=1$
\end{enumerate}
		\end{multicols}
  \item The value of the integral
$$
\oint_{C} \frac{z^{2}}{e^{z}+1} d z
$$
where $C$ is the circle $|z|=4$, is
\begin{enumerate}
    \item $2 \pi i$
    \item $2 \pi^{2} i$
    \item $4 \pi^{2} i$
    \item $4 \pi^{2} i$
\end{enumerate}
  \item   A ray of light inside Region 1 in the $x y$-plane is incident at the semicircular boundary that carries no free charges. The electric field at the point $P\left(r_{0}, \pi / 4\right)$ in plane polar coordinates is $\vec{E}_{1}=7 \hat{e}_{r}-3 \hat{e}_{\varphi}$, where $\hat{e}_{r}$ and $\hat{e}_{\varphi}$ are the unit vectors. The emerging ray in Region 2 has the electric field $\vec{E}_{2}$ parallel to $x$ - axis. If $\varepsilon_{1}$ and $\varepsilon_{2}$ are the dielectric constants of Region 1 and Region 2 respectively, then $\frac{\varepsilon_{2}}{\varepsilon_{1}}$ is
  \input{figs/fig1.tex}
  
  
\item     The solution of the differential equation
$$
\frac{d^{2} y}{d t^{2}}-y=0
$$
subject to the boundary conditions $y(0)=1$ and $y(\infty)=0$, is
\begin{multicols}{4}
			\begin{enumerate}

\item $\cos t+\sin t$
\item $\cosh t+\sinh t$
\item $\cos t-\sin t$
\item  $\cosh t-\sinh t$
   \end{enumerate}
		\end{multicols}
  \item Given that the linear transformation of a generalized coordinate $q$ and the corresponding momentum $p$,
$$
\begin{gathered}
Q=q+4 a p \\
P=q+2 p
\end{gathered}
$$
is canonical, the value of the constant $a$ is $\qquad$ .

  \item The value of the magnetic field required to maintain non-relativistic protons of energy 1 MeV in a circular orbit of radius 100 mm is $\qquad$ Tesla.
(Given: $m_{p}=1.67 \times 10^{-27} {~kg}, e=1.6 \times 10^{-19} {C}$ )

\item  For a system of two bosons, each of which can occupy any of the two energy levels 0 and $\varepsilon$, the mean energy of the system at a temperature $T$ with $\beta=\frac{1}{k_{B} T}$ is given by
 \begin{multicols}{4}
			\begin{enumerate}
   
 
   \item$\frac{\varepsilon e^{-\beta \varepsilon}+2 \varepsilon e^{-2 \beta \varepsilon}}{1+2 e^{-\beta \varepsilon}+e^{-2 \beta \varepsilon}}$
\item  $\frac{1+\varepsilon e^{-\beta \varepsilon}}{2 e^{-\beta \varepsilon}+e^{-2 \beta \varepsilon}}$
\item  $\frac{2 \varepsilon e^{-\beta \varepsilon}+\varepsilon e^{-2 \beta \varepsilon}}{2+e^{-\beta \varepsilon}+e^{-2 \beta \varepsilon}}$
\item $\frac{\varepsilon e^{-\beta \varepsilon}+2 \varepsilon e^{-2 \beta \varepsilon}}{2+e^{-\beta \varepsilon}+e^{-2 \beta \varepsilon}}$
 \end{enumerate}
	\end{multicols}
  \item In an interference pattern formed by two coherent sources, the maximum and the minimum of the intensities are $9 I_{0}$ and $I_{0}$, respectively. The intensities of the individual waves are
  

\begin{multicols}{4}
			\begin{enumerate}
   \item $3 I_{0}$ and $I_{0}$
\item  $4 I_{0}$ and $I_{0}$
\item $5 I_{0}$ and $4 I_{0}$
\item $9 I_{0}$ and $I_{0}$
\end{enumerate}
		\end{multicols}
  \item  $\quad \psi_{1}$ and $\psi_{2}$ are two orthogonal states of a spin $\frac{1}{2}$ system. It is given that
$$
\psi_{1}=\frac{1}{\sqrt{3}}\myvec{{1}\\{0}}+\sqrt{\frac{2}{3}}\myvec{{0}\\{1}}
$$
where $\myvec{{1}\\{0}}$ and $\myvec{{0} \\{1}}$ represent the spin-up and spin-down states, respectively. When the system is in the state $\psi_{2}$, its probability to be in the spin-up state is $\qquad$ .
 
			
		
 \end{enumerate}

\end{document}
